Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review

### 2021-01-28 manuscript.Rmd
revisions

---
title             : "Mapping correlates of adolescent emotion dysregulation: A text-mining based systematic review"
shorttitle        : "ADOLESCENT EMOTION DYSREGULATION"

@@

abstract: |
  Adolesence is a developmentally sensititve period for emotion dysregulation.
  Although substantial empirical research has addressed relevant risk factors,
  the literature is fragmented across subdisciplines, and
  an integrating framework is lacking.
  This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 
  10-25) emotion dysregulation. First, we established a baseline of relevant terms gleaned from 
  theory and recent narrative reviews. Then, we conducted two text mining analyses to examine 
  term/document frequency and co-occurrence in author-provided keywords and abstracts. Results 
  reﬂected constructs commonly featured in theory and narrative reviews, but also identified 
  underrepresented themes. This research constitutes a first step towards integrating the 
  literature, and illustrates how text mining reviews may complement narrative reviews.

wordcount         : "6311"
bibliography      : ["veni_sysrev.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man,noextraspace"
output            : papaja::apa6_docx
knit              : worcs:::cite_essential
header-includes:
  - \raggedbottom
---

```{r setup, include = FALSE}
library("papaja")
library(data.table, quietly = TRUE, warn.conflicts = FALSE)
library(knitr)
library(kableExtra)
library(cowplot)
run_everything <- TRUE
notingraph <- list()
keyw <- function(x){
  x
}
```
<!-- Reviewer suggestions:
Kristin Buss -->

@@

A key developmental challenge in adolescence is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
as one in five individuals, adolescence marks the onset of emotion
regulation-related mental illness, which can persist throughout the life course
[see @leeAdolescentMentalHealth2014]. 
It is therefore crucial to identify which
risk factors and environmental hazards render some adolescents more susceptible
to emotional difficulties than others. <!--SH: Main goal of paper -->
Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, because the topic has been investigated from different (sub)disciplines.
As a result, there is a lack of unifying theory,
and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].

@@

## Why adolescence is an important life stage for emotion regulation

Adolescence is defined as a life stage ranging from pubertal onset to
adult-like independence [@steinbergAgeOpportunityLessons2014].
It is thus demarcated by both biological and socio-cultural factors.
It has been argued that,
due to accellerated pubertal onset and delayed transitions to adult roles,
adolescence now ranges from 10-24 years in the modern Western world
[@sawyerAgeAdolescence2018].
<!-- From Barriola:
* adolescence, more than adulthood or childhood, is characterized by frequent
and intense emotions (Larson et al. 1980; Larson and Lampmanpetraitis 1989).
* signi?cant psychosocial changes that call for an increase in sophistication
of ER strategies (Steinberg 2005)
* novel stressors associated with social relationships, including pressures to
conform to adult expectations relating to maturity, educational achievement,
gender appropriate conduct, and other socially competent behaviors (Yap et al.
2007)
* Additionally, adolescents have an increased orientation toward autonomy
(Spear 2000) including autonomous emotional regulation-->
Adolescence is increasingly seen as a developmentally sensitive period for
mature emotion regulation skills. During this period, children experience rapid
biological, cognitive, and social changes that prompt new emotional
experiences, and tax existing regulatory abilities
[@steinbergAgeOpportunityLessons2014]. At the same time, the staggered
development of motivational-emotional and regulatory brain circuits gives rise
to a maturity gap [@croneUnderstandingAdolescencePeriod2012]. 
This leads youngsters to pursue new experiences in life and love,
without being fully prepared to cope with the emotional outcomes.
Due to these coalescing changes,
adolescents display a restricted repertoire of emotion regulation strategies
compared to younger or older individuals
[@zimmermannEmotionRegulationEarly2014]. Consequently, adolescents experience
more frequent and intense (negative) emotions than children or adults [see
@silkAdolescentsEmotionRegulation2003]. The literature thus paints a picture of
adolescence as a chrysalis for emotional development: Children enter this stage
with emotion regulation skills adapted to the challenges of childhood. During
adolescence, emotional systems are rearranged substantially. These changes
render adolescents temporarily vulnerable to emotional dysregulation, but
ultimately serve a functional role in acquiring mature emotion regulation
skills. Eventually, most adolescents emerge ready to take on the challenges of
early adulthood. Unfortunately, a sizeable proportion of adolescents instead
manifests enduring emotional difficulties [@leeAdolescentMentalHealth2014].

<!--
* intense negative emotions in daily life (Silk, Steinberg, & Morris, 2003) 
* unstable peer or romantic relationships (Furman & Collins, 2009)
* decrease in perceived support from parents (Furman & Buhrmester, 1992).
* early adolescence is characterized by a higher rate of conflicts with parents (Laursen, Coy, & Collins, 1998)
* higher variability of negative emotions compared to late adolescence (Larson, Moneta, Richards, & Wilson, 2002).
* relative to other developmental stages, adolescence involves a particularly large number of transitions, novel situations, and new stimuli, physical, cognitive, emotional, and social development—particularly in early and mid-adolescence (Seiffge-Krenke, 2000)
-->

## The consequences of difficulties in emotion regulation

<!--Acquiring mature emotion regulation abilities is important, because t-->The
consequences of difficulties in emotion regulation are extensive,
well-documented, and persist throughout the life course. Meta-analyses indicate
that such difficulties are associated with internalizing, and to a lesser extent, externalizing, psychopathology
[@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017]. 
Individuals who engage in maladaptive
emotion regulation strategies also experience more negative emotions,
diminished well-being, and greater strain in interpersonal relationships
[@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
<!--Adolescence also appears to be a key period for developing mature emotion
regulation skills - but not all adolescents do so successfully. As many as one
in five adolescents instead develop severe emotional difficulties.--> 
Given the
prevalence of emotional difficulties and their implications for
individual mental health, wellbeing, and social functioning, and their downstream
cost to society as a whole [@leeAdolescentMentalHealth2014], it is essential to
have a solid understanding of the risk factors associated with adolescents'
emotion regulation difficulties.

@@

Our text mining analysis of the empirical literature is best understood against a backdrop of the existing theoretical landscape.
We therefore provide a summary theoretical review.
Other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
The correlates of emotion regulation difficulties discussed in our theoretical review
are summarized in Figure \@ref(fig:baseline)^[Based on an author-curated list of keywords, caterogized using the dictionary method introduced in Analysis 1.].

```{r baseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel). Transparent circles indicate constructs also represented in the theory."}
source("baseline.R", local = TRUE)
knitr::include_graphics("baseline_network.png") 
#fig_svg <- cowplot::ggdraw()+cowplot::draw_image("s1_varimp.svg")
#plot(fig_svg)

@@

<!--
Note that the left panel of Figure \@ref(fig:baseline) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
The left panel of Figure \@ref(fig:baseline) summarizes key constructs covered by the theories reviewed above. 
In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
This allows us to see in what respects the text mining analysis reflects existing theory,
and in what respects it complements it.-->

@@

Whereas theory provides a top-down frame of reference,
literature reviews can provide a bottom-up, inductive understanding of a phenomenon.
Given the noted absence of a single overarching theory, reviews might provide additional
insight into factors considered relevant in the etiology of adolescents'
emotion regulation competencies. 
Innovative text mining methods are promising in this respect, because they can comprehensively review the available literature.
Narrative reviews, however, constitute the status quo.
We will therefore examine how two excellent narrative reviews on emotion regulation in adolescence complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
Figure \@ref(fig:baseline) visualizes constructs uniquely covered by these narrative reviews,
relative to the theoretical literature.

<!--
Note that the left panel of Figure \@ref(fig:baseline) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
The left panel of Figure \@ref(fig:baseline) summarizes key constructs covered by the theories reviewed above. 
In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
This allows us to see in what respects the text mining analysis reflects existing theory,
and in what respects it complements it.-->

@@

A recent review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
discussion of several issues that complement prior publications.
This includes the implications of physiological changes,
including neurocognitive development and pubertal maturation.
Conflict with parents is addressed too, which peaks when adolescents become increasingly individuated.
Such conflict impacts both day-to-day mood swings and dispositional emotion dysregulation [see also
@vanlissaCostEmpathyParentadolescent2017].
Adolescents also become increasingly oriented towards peers.
This increases sensitivity to social status and norms,
along with concomitant increases in peer pressure and risk taking.
Pubertal development further precipitates sexual and romantic behavior,
and the intensification of both biological sex differences and gender stereotyped behavior.
<!--With regard to the process of emotion regulation,
Coe-Odess and colleagues discuss the importance
of strategies, and point out that, in addition to negative emotionality,
positive emotionality also peaks in adolescence. -->
Relatedly, the authors describe how hormonal changes intensify the stress response,
which helps explain adolescents' greater susceptibility to emotion dysregulation.
Finally, <!--going beyond the implications of cognitive development
discussed in other publications,--> the authors discuss how cognitive development and increased capacity
for abstract thought relate to identity formation - a key challenge in
adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
understanding, and by extension, empathy [see also
@vanlissaLongitudinalInterplayAffective2014].

As can be seen in Figure \@ref(fig:baseline), 
there are notable parallels between correlates of emotion regulation identified in these
narrative reviews, and in the preceding theoretical literature.
Nevertheless,
these literature reviews also touch upon issues that have received little
attention in theoretical work.
<!--These include specific individual differences at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
Further introduced are proximal influences, including the role of media, norms, and social status.-->
This illustrates that reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
An important limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
We seek to complement preceding work by using text mining to conduct a more comprehensive empirical
literature review, and map the factors associated with adolescent emotion
regulation.

@@

The present paper aims to map the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
First, we conducted a systematic search to
elicit a corpus of relevant literature. Second, we used text mining techniques
to extract relevant constructs from the corpus. Third, we used a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we mapped interrelations between these constructs. Fifth, we classified
contstructs as potential predictors or outcomes.
We used the Workflow for Open Reproducible Code in Science (WORCS)
to ensure transparency and  reproducibility. All code and data are available online at [masked].

@@

We searched Web of Science,
the most comprehensive database for which we had permissions to export keywords and abstracts.
The search strategy was based on
procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
constructed a reference set of 29 articles.
Then we constructed a search string to retrieve this set.
The search string consisted of synonyms of emotion regulation and adolescence.
It returned 6653 results, including 25 records in the reference set.
To match all 29 reference set items required adding the terms `"emotio* socialization" OR "emotio* processes"` as synonyms for emotion regulation.
Doing so resulted in 191 more hits, most of which did not meet the inclusion criteria explained below.
We thus deemed these terms to be overly inclusive, and
proceeded with the original search string above.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  library(bibliometrix)
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

@@

if(!file.exists("recs_final.csv")){
  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
  write.csv(recs_final, "recs_final.csv", row.names = FALSE)
} else {
  recs_final <- read.csv("recs_final.csv")
}
```
The screening and deduplication procedure is detailed in Figure \@ref(fig:prismachart).
Duplicates were identified using DOI and title similarity.
Papers were screened based on two main criteria:
They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24).
Preliminary screening was conducted in Rayyan QRCI [@Ouzzani2016].
After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview [@van_de_schoot_rens_2020_3828293].
This program uses machine learning to screen articles.
We trained the machine learning algorithm by manually screening an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers, until - among the most recently screened 100 papers - only 6 were excluded.
In total, `r nrow(recs_final)` papers were deemed suitable for analysis.

```{r prismachart, results='asis', fig.cap="Record screening flowchart"}
if(!isTRUE(tools::md5sum("prismachart.png") == "08351426aee2005edd1332a32b958ea0" )){
  library(tidySEM)

@@

  p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3, text_size = 4)
  ggsave("prismachart.png", p, device = "png")
  ggsave("prismachart.svg", p, device = "svg")
}

@@

  svg("s1_varimp.svg", width = 7/2.54, height = 14/2.54)
  eval(p)
  dev.off()

@@

@@

  # Save files
  png("study1_network1.png", width = 960)
  eval(p)
  dev.off()

>>>>

---
title             : "Mapping correlates of adolescent emotion regulation: A text-mining based systematic review"
shorttitle        : "ADOLESCENT EMOTION REGULATION"

@@

abstract: |
  Adolesence is a developmentally sensititve period for emotion regulation.
  Although substantial empirical research has addressed relevant risk factors,
  the literature is fragmented across subdisciplines, and
  an integrating framework is lacking.
  This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 
  10-25) emotion regulation. First, we established a baseline of relevant terms gleaned from 
  theory and recent narrative reviews. Then, we conducted two text mining analyses to examine 
  term/document frequency and co-occurrence in author-provided keywords and abstracts. Results 
  reﬂected constructs commonly featured in theory and narrative reviews, but also identified 
  underrepresented themes. This research constitutes a first step towards integrating the 
  literature, and illustrates how text mining reviews may complement narrative reviews.
keywords          : "emotion regulation, adolescence, systematic review, text mining, machine
learning"
wordcount         : "6311"
bibliography      : ["veni_sysrev.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man,noextraspace"
output            : papaja::apa6_docx
knit              : worcs:::cite_essential
header-includes:
  - \raggedbottom
---

```{r setup, include = FALSE}
library("papaja")
library(data.table, quietly = TRUE, warn.conflicts = FALSE)
library(knitr)
library(kableExtra)
library(cowplot)
run_everything <- FALSE
notingraph <- list()
keyw <- function(x){
  x
}
```
<!-- Reviewer suggestions:
Kristin Buss -->

@@

A key developmental challenge in adolescence is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
as one in five individuals, adolescence marks the onset of
emotion regulation difficulties and associated mental health problems,
which can persist throughout the life course
[see @leeAdolescentMentalHealth2014]. 
It is therefore crucial to identify which
risk factors and environmental hazards render some adolescents more susceptible
to emotional difficulties than others. <!--SH: Main goal of paper -->
Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, because the topic has been investigated from different (sub)disciplines.
As a result, there is a lack of unifying theory,
and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].

@@

## Relevance and scope

Adolescence is a life stage defined by biological and socio-cultural factors,
ranging from pubertal onset to adult-like independence [approximately 10-24 years of age, @steinbergAgeOpportunityLessons2014; @sawyerAgeAdolescence2018].
It constitutes a developmentally sensitive period for
mature emotion regulation skills, during which children experience
biological, cognitive, and social changes that prompt new emotional
experiences and tax regulatory abilities [@steinbergAgeOpportunityLessons2014].
<!-- At the same time, the staggered development of motivational-emotional and regulatory brain circuits gives rise
to a maturity gap [@croneUnderstandingAdolescencePeriod2012]. 
This leads youngsters to pursue new experiences in life and love,
without being fully prepared to cope with the emotional outcomes. --> 
Due to these coalescing changes,
adolescents display a restricted repertoire of emotion regulation strategies
compared to younger or older individuals
[@zimmermannEmotionRegulationEarly2014].
Consequently, adolescents experience more frequent and intense (negative) emotions than children or adults [see @silkAdolescentsEmotionRegulation2003].
<!--The literature thus paints a picture of
adolescence as a chrysalis for emotional development: Children enter this stage
with emotion regulation skills adapted to the challenges of childhood. During
adolescence, emotional systems are rearranged substantially.-->
Eventually, most adolescents emerge ready to take on the challenges of
early adulthood. Unfortunately, a sizable proportion of adolescents instead
manifests enduring emotional difficulties [@leeAdolescentMentalHealth2014].
<!--
* intense negative emotions in daily life (Silk, Steinberg, & Morris, 2003) 
* unstable peer or romantic relationships (Furman & Collins, 2009)
* decrease in perceived support from parents (Furman & Buhrmester, 1992).
* early adolescence is characterized by a higher rate of conflicts with parents (Laursen, Coy, & Collins, 1998)
* higher variability of negative emotions compared to late adolescence (Larson, Moneta, Richards, & Wilson, 2002).
* relative to other developmental stages, adolescence involves a particularly large number of transitions, novel situations, and new stimuli, physical, cognitive, emotional, and social development—particularly in early and mid-adolescence (Seiffge-Krenke, 2000)
-->
According to meta-analyses, such difficulties in emotion regulation are associated with
extensive and persist internalizing, and to a lesser extent, externalizing, psychopathology
[@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017]. 
Individuals who engage in maladaptive
emotion regulation strategies also experience more negative emotions,
diminished well-being, and greater strain in interpersonal relationships
[@grossIndividualDifferencesTwo2003a; @bellRelationshipsInputsOutputs2000].
<!--Adolescence also appears to be a key period for developing mature emotion
regulation skills - but not all adolescents do so successfully. As many as one
in five adolescents instead develop severe emotional difficulties.--> 
Given the
prevalence of emotional difficulties and their implications for
individual mental health, wellbeing, and social functioning, and their downstream
cost to society as a whole [@leeAdolescentMentalHealth2014], it is essential to
have a solid understanding of the risk factors associated with adolescents'
emotion regulation difficulties.

@@

```{r baselinecode, message=FALSE, echo = FALSE, warning = FALSE, error=FALSE, results='hide'}
library(data.table)
library(stringr)
library(udpipe)
library(igraph)
library(wordcloud)
library(Matrix)
library(ggplot2)
library(yaml)
source("word_functions.R")
source("circle2.R")
dict <- read_yaml("yaml_dict.txt")

  bl_theory <- readLines("baseline_theory.txt")
  bl_review <- readLines("baseline_reviews.txt")
  df <- data.frame(word = trimws(tolower(bl_theory)), source = "theory")
  df <- rbind(df, data.frame(word = trimws(tolower(bl_review)), source = "reviews"))
  # Categorize words
  res_cat <- cat_words(df$word, dict, handle_dups = "all")
  df$cat <- res_cat$words
  df <- df[!duplicated(df$cat), ]
  if(!is.null(res_cat[["unmatched"]])){
    df <- df[!df$cat %in% names(res_cat$unmatched), ]
  }

  baseline_cat <- df
  baseline <- c("dysregulation", unique(df$cat[df$source == "theory"]))

  saveRDS(baseline, "baseline.RData")
  saveRDS(baseline_cat, "baseline_cat.RData")

in_theory <- df$word[df$source == "theory"]
in_rev <- df$word[!df$source == "theory"]
in_rev[!in_rev %in% in_theory]

df_plot <- data.frame(term1 = df$cat[df$source == "theory"], term2 = "dysregulation")
df_plot <- df_plot[!df_plot$term1 == df_plot$term2, ]
edg <- df_plot

edg$width = 1

vert <- data.frame(name = unique(c(df_plot$term1, df_plot$term2)), label = pretty_words(unique(c(df_plot$term1, df_plot$term2))), size = 1)
vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]

categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
if(any(!vert$name %in% categ$name)){
  write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
  stop("Please re-categorize missing vertices.")
} 
vert$Category <- categ$category[match(vert$name, categ$name)]

cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "forestgreen")
cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
vert$color <- cat_cols[vert$Category]
vert$frame.color <- cat_cols[vert$Category]
#min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
vert$size <- scales::rescale(log(vert$size), c(4, 12))
g1 <- graph_from_data_frame(edg, vertices = vert,
                           directed = FALSE)
#g <- Rsenal::pruneEdg
#min_size <- (strwidth(vert$label[max(nchar(vert$label))]) + strwidth("oo"))*100

# edge thickness
#E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(2, 8))

# Plot 2 ------------------------------------------------------------------

df_plot <- data.frame(term1 = df$cat, term2 = "dysregulation", source = df$source)

edg <- df_plot

edg$width = 1

vert <- data.frame(name = unique(c(df_plot$term1, df_plot$term2)), label = pretty_words(unique(c(df_plot$term1, df_plot$term2))), size = 1)
vert <- vert[vert$name %in% unique(c(edg$term1, edg$term2)), ]

categ <- read.csv("study1_categorization.csv", stringsAsFactors = FALSE)
if(any(!vert$name %in% categ$name)){
  write.table(vert$name[!vert$name %in% categ$name], "clipboard", sep = "\n", row.names = FALSE, col.names= FALSE)
  stop("Please re-categorize missing vertices.")
} 
vert$Category <- categ$category[match(vert$name, categ$name)]
vert$faded <- vert$name %in% df$cat[df$source == "theory"]
cat_cols <- c(Outcome = "gray50", Indicator = "tomato", Cause = "gold", Protective = "olivedrab2")
vert$color <- cat_cols[vert$Category]
vert$frame.color <- cat_cols[vert$Category]
# cat_cols <- c(Outcome = "#E5E5E5", Indicator = "#FFC9AD", Cause = "#FFFF66", Protective = "#E6FF6D")
vert$color[vert$faded] <- "#FFFFFF"#cat_cols[vert$Category[vert$faded]]

#min_size <- (strwidth(vert$name[max(nchar(vert$name))]) + strwidth("oo")) * 100
vert$size <- scales::rescale(log(vert$size), c(4, 12))
g2 <- graph_from_data_frame(edg, vertices = vert,
                           directed = FALSE)
#g <- Rsenal::pruneEdg
#min_size <- (strwidth(vert$label[max(nchar(vert$label))]) + strwidth("oo"))*100

# edge thickness
#E(g)$width <- scales::rescale(sqrt(E(g)$width), to = c(2, 8))

set.seed(2) #4 #2 #3
l1 <- l <- layout_with_fr(g1)
set.seed(33)
l2 <- layout_with_fr(g2)

p <- quote({
  # Set margins to 0
  par(mar=c(0,0,0,0),
      mfrow=c(1,2))
  plot(g1, edge.curved = 0, layout=l1,
       vertex.label.family = "sans",
       vertex.label.cex = 0.8,
       vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
  legend(x=-1.1, y=1.1, names(cat_cols), pch=21, col=cat_cols, pt.bg=cat_cols, pt.cex=2, cex=.8, bty="n", ncol=1)
  plot(g2, edge.curved = 0, layout=l2,
       vertex.label.family = "sans",
       vertex.label.cex = 0.8,
       vertex.shape = "circle2",
       #vertex.frame.color = 'gray40',
       vertex.label.color = 'black',      # Color of node names
       vertex.label.font = 1,         # Font of node names
       vertex.frame.width = 2
  )
})
saveRDS(g1, "bl_g1.RData")
saveRDS(g2, "bl_g2.RData")
saveRDS(l1, "bl_l1.RData")
saveRDS(l2, "bl_l2.RData")
# Save files
png("baseline_network.png", width = 960)
eval(p)
dev.off()

svg("baseline_network.svg", width = 14)
eval(p)
dev.off()
```

```{r baseline, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (left panel) and narrative reviews (right panel). Transparent circles indicate constructs also represented in the theory."}
knitr::include_graphics("baseline_network.png") 
```
```{r allnetworks, warning=FALSE, eval = TRUE, results='asis', out.width = "100%", fig.cap="Correlates of emotion regulation difficulties according to theory (A), narrative reviews (B), and term co-occurrence in author keywords (C) and abstracts (D). Size of lines and circles represents frequency. Dashed lines represent links not involving dysregulation. Transparent circles indicate constructs also represented in the theory (panel A)."}

knitr::include_graphics("networks.png") 
```

Our text mining analysis of the empirical literature is best understood against a backdrop of the existing theoretical landscape.
We therefore provide a summary theoretical review.
Other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].

@@

<!--
Note that the left panel of Figure \@ref(fig:allnetworks) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
The left panel of Figure \@ref(fig:allnetworks) summarizes key constructs covered by the theories reviewed above. 
In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
This allows us to see in what respects the text mining analysis reflects existing theory,
and in what respects it complements it.-->

@@

Whereas theory provides a top-down frame of reference,
literature reviews can provide a bottom-up, inductive understanding of a phenomenon.
Given the noted absence of a single overarching theory, reviews might provide additional
insight into factors considered relevant in the etiology of adolescents'
emotion regulation competencies. 
Innovative text mining methods are promising in this respect, because they can comprehensively review the available literature.
Narrative reviews, however, constitute the status quo.
We will therefore examine how two excellent narrative reviews on emotion regulation in adolescence complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
Figure \@ref(fig:allnetworks) visualizes constructs uniquely covered by these narrative reviews,
relative to the theoretical literature.

<!--
Note that the left panel of Figure \@ref(fig:allnetworks) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
The left panel of Figure \@ref(fig:allnetworks) summarizes key constructs covered by the theories reviewed above. 
In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
This allows us to see in what respects the text mining analysis reflects existing theory,
and in what respects it complements it.-->

@@

A recent review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
discussion of several issues that complement prior publications.
This includes the implications of physiological changes,
including neurocognitive development and pubertal maturation.
Conflict with parents is addressed too, which peaks when adolescents become increasingly individuated.
Such conflict impacts both day-to-day mood swings and dispositional emotion regulation difficulties [see also
@vanlissaCostEmpathyParentadolescent2017].
Adolescents also become increasingly oriented towards peers.
This increases sensitivity to social status and norms,
along with concomitant increases in peer pressure and risk taking.
Pubertal development further precipitates sexual and romantic behavior,
and the intensification of both biological sex differences and gender stereotyped behavior.
<!--With regard to the process of emotion regulation,
Coe-Odess and colleagues discuss the importance
of strategies, and point out that, in addition to negative emotionality,
positive emotionality also peaks in adolescence. -->
Relatedly, the authors describe how hormonal changes intensify the stress response,
which helps explain adolescents' greater susceptibility to emotion regulation difficulties.
Finally, <!--going beyond the implications of cognitive development
discussed in other publications,--> the authors discuss how cognitive development and increased capacity
for abstract thought relate to identity formation - a key challenge in
adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
understanding, and by extension, empathy [see also
@vanlissaLongitudinalInterplayAffective2014].

As can be seen in Figure \@ref(fig:allnetworks), 
there are notable parallels between correlates of emotion regulation identified in these
narrative reviews, and in the preceding theoretical literature.
Nevertheless,
these literature reviews also touch upon issues that have received little
attention in theoretical work.
<!--These include specific individual differences at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
Further introduced are proximal influences, including the role of media, norms, and social status.-->
This illustrates that reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
An important limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
We seek to complement preceding work by using text mining to conduct a more comprehensive empirical
literature review, and map the factors associated with adolescent emotion
regulation.

@@

The present paper aims to map the constructs
related to adolescent emotion regulation, based on a systematic review of
the literature. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
First, we conducted a systematic search to
elicit a corpus of relevant literature. Second, we used text mining techniques
to extract relevant constructs from the corpus. Third, we used a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we mapped interrelations between these constructs. Fifth, we classified
contstructs as potential predictors or outcomes.
We used the Workflow for Open Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020]
to ensure transparency and  reproducibility. All code and data are available online at [masked].

@@

We searched Web of Science,
the most comprehensive database for which we had permissions to export keywords and abstracts.
The search strategy was based on
procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
constructed a reference set of 29 articles.
Then we constructed a search string to retrieve this set.
The search string consisted of synonyms of emotion regulation and adolescence.
It returned 6653 results, including 25 records in the reference set.
To match all 29 reference set items required adding the terms `"emotio* socialization" OR "emotio* processes"` as synonyms for emotion regulation.
Doing so resulted in 191 more hits, most of which did not meet the inclusion criteria explained below.
We thus deemed these terms to be overly inclusive, and
proceeded with the original search string.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  library(bibliometrix)
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

@@

if(!file.exists("recs_final.csv")){
  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
  write.csv(recs_final, "recs_final.csv", row.names = FALSE)
} else {
  recs_final <- read.csv("recs_final.csv")
}
```

Starting with all `r nrow(recs)` records identified through Web of Science,
we removed duplicates based on DOI matches (n = 2) and title similarity (n = 54).
Rayyan QRCI [@Ouzzani2016] identified an additional 13 duplicates.
We then screened papers based on two main criteria:
They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24).
Preliminary screening was conducted in Rayyan.
After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers (`r sum(screen$rayyan == "False")` excluded),
we continued screening in ASReview [@van_de_schoot_rens_2020_3828293].
This program uses machine learning to screen articles.
We trained the naive Bayes algorithm by manually screening an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers (`r sum(screen$included == 1, na.rm = TRUE)-sum(screen$rayyan == "False")` excluded), until among the most recently screened 100 papers only 6 were excluded.
In total, `r nrow(recs_final)` papers were deemed suitable for analysis.

```{r prismachart, eval = FALSE, results='asis', fig.cap="Record screening flowchart"}
if(!isTRUE(tools::md5sum("prismachart.png") == "08351426aee2005edd1332a32b958ea0" )){
  library(tidySEM)

@@

  p <- graph_sem(layout = lo, nodes = nodes, edges = edges, angle = 1, rect_height = 1.2, rect_width = 1.3, text_size = 4)
  ggsave("prismachart.png", p, device = "png", width = 7, height = 4)
  ggsave("prismachart.svg", p, device = "svg", width = 7, height = 4)
}

@@

  saveRDS(p, "s1_varimp.RData")  
  svg("s1_varimp.svg", width = 7/2.54, height = 14/2.54)
  eval(p)
  dev.off()

@@

  p1 <- p + theme(legend.position = "none")

@@

  # Save files
  saveRDS(g, "s1_g1.RData")
  saveRDS(l1, "s1_l1.RData")

  png("study1_network1.png", width = 960)
  eval(p)
  dev.off()
